Robust Deluding Adversarial Examples

### 2019-05-08 minutia/paper.tex

\subsection{Attacks Based upon Fast Gradient Sign Method}

@@

We define $s_\eta$ as the perturbed observation:
\begin{equation}
    s_\eta = (1 + \epsilon) s
\end{equation}

Let $s_\eta$ be the perturbed observation and $s_c$ scaled observation, so we are trying to find the following:
\begin{equation}
\begin{aligned}
& \underset{s}{\argmin}
& & {\norm{s_\eta - s_c}}
\end{aligned}
\end{equation}
which is the state observation that have the minimum distance between real-world [scaled] observation and the perturbed one.

@@

\subsection{Reward Perturbation Attacks}
In an adversarial environment we try to perturb reward to interfere in learning process of the RL agent. We considered this attack also in scenarios with a single reward which we will show the process later.

>>>>

\subsection{Observation-perturbed attacks}

@@

We define $s_\eta$ as the perturbed observation:
\begin{equation}
    s_\eta = s . (1 + \epsilon) 
\end{equation}

Let $s_\eta$ be the perturbed observation and $s_c$ scaled observation, so we are trying to find the following:
\begin{equation}
\begin{aligned}
& \underset{s}{\argmin}
& & {\norm{s_\eta - s_c}} = \norm{s . (1 + \eps) - s_c}
\end{aligned}
\end{equation}
which is the state observation that have the minimum distance between real-world [scaled] observation and the perturbed one.

@@

\subsection{Reward-Perturbed attacks}
In an adversarial environment we try to perturb reward to interfere in learning process of the RL agent. We considered this attack also in scenarios with a single reward which we will show the process later.
